---
title: "Lecture notes"
---

+ Chapter 1: 
  + Parametric and Nonparametric Methods 
```{r, echo=FALSE, out.width = '800px', out.height = '400px', results='asis'}
cat('<embed src="./Lecture notes/Chapter 1_1.pdf" 
    type="application/pdf" 
    width="100%" height="400px" />')
```
  + Binomial problem 
```{r, echo=FALSE, out.width = '800px', out.height = '400px', results='asis'}
cat('<embed src="./Lecture notes/Chapter 1_2.pdf" 
    type="application/pdf" 
    width="100%" height="400px" />')
```

+ Chapter 2: 
  + Wilcoxon Signed Rank Test 
```{r, echo=FALSE, out.width = '800px', out.height = '400px', results='asis'}
cat('<embed src="./Lecture notes/Chapter 2_1.pdf" 
    type="application/pdf" 
    width="100%" height="400px" />')
```

  + Signed Test 
```{r, echo=FALSE, out.width = '800px', out.height = '400px', results='asis'}
cat('<embed src="./Lecture notes/Chapter 2_2.pdf" 
    type="application/pdf" 
    width="100%" height="400px" />')
```

  + A Comparison of Statistical Tests  
```{r, echo=FALSE, out.width = '800px', out.height = '400px', results='asis'}
cat('<embed src="./Lecture notes/Chapter 2_3.pdf" 
    type="application/pdf" 
    width="100%" height="400px" />')
```

  + Paired Comparisons  
```{r, echo=FALSE, out.width = '800px', out.height = '400px', results='asis'}
cat('<embed src="./Lecture notes/Chapter 2_4.pdf" 
    type="application/pdf" 
    width="100%" height="400px" />')
```

+ Chapter 3: 
  + Two-Sample Permutation Test 
```{r, echo=FALSE, out.width = '800px', out.height = '400px', results='asis'}
cat('<embed src="./Lecture notes/Chapter 3_1.pdf" 
    type="application/pdf" 
    width="100%" height="400px" />')
```

  + Wilcoxon Rank-Sum Test 
```{r, echo=FALSE, out.width = '800px', out.height = '400px', results='asis'}
cat('<embed src="./Lecture notes/Chapter 3_2.pdf" 
    type="application/pdf" 
    width="100%" height="400px" />')
```

` + Why ranks? Scoring systems
```{r, echo=FALSE, out.width = '800px', out.height = '400px', results='asis'}
cat('<embed src="./Lecture notes/Chapter 3_3.pdf" 
    type="application/pdf" 
    width="100%" height="400px" />')
```

  + Tests for Equality of Scale Parameters 
```{r, echo=FALSE, out.width = '800px', out.height = '400px', results='asis'}
cat('<embed src="./Lecture notes/Chapter 3_4.pdf" 
    type="application/pdf" 
    width="100%" height="400px" />')
```

  + Kolmogorov-Smirnov test
```{r, echo=FALSE, out.width = '800px', out.height = '400px', results='asis'}
cat('<embed src="./Lecture notes/Chapter 3_5.pdf" 
    type="application/pdf" 
    width="100%" height="400px" />')
```

+ Chapter 4: 
  + Kruskal-Wallis Test
```{r, echo=FALSE, out.width = '800px', out.height = '400px', results='asis'}
cat('<embed src="./Lecture notes/Chapter 4_1.pdf" 
    type="application/pdf" 
    width="100%" height="400px" />')
```

  + Jonckheere-Terpstra Test for Ordered Alternatives 
```{r, echo=FALSE, out.width = '800px', out.height = '400px', results='asis'}
cat('<embed src="./Lecture notes/Chapter 4_2.pdf" 
    type="application/pdf" 
    width="100%" height="400px" />')
```

  + Fligner-Wolfe Test for Treatments versus a Control 
```{r, echo=FALSE, out.width = '800px', out.height = '400px', results='asis'}
cat('<embed src="./Lecture notes/Chapter 4_3.pdf" 
    type="application/pdf" 
    width="100%" height="400px" />')
```

  + Multiple Comparisons
```{r, echo=FALSE, out.width = '800px', out.height = '400px', results='asis'}
cat('<embed src="./Lecture notes/Chapter 4_4.pdf" 
    type="application/pdf" 
    width="100%" height="400px" />')
```

  + Two-Sided All-Treatments Multiple Comparisons for General Alternative  
```{r, echo=FALSE, out.width = '800px', out.height = '400px', results='asis'}
cat('<embed src="./Lecture notes/Chapter 4_5.pdf" 
    type="application/pdf" 
    width="100%" height="400px" />')
```

  + One-Sided All-Treatments Multiple Comparisons for Ordered Treatment Effects Alternatives 
```{r, echo=FALSE, out.width = '800px', out.height = '400px', results='asis'}
cat('<embed src="./Lecture notes/Chapter 4_6.pdf" 
    type="application/pdf" 
    width="100%" height="400px" />')
```

  + One-Sided Treatments-versus-Control Multiple Comparisons for Treatment-versus-Control Alternatives
```{r, echo=FALSE, out.width = '800px', out.height = '400px', results='asis'}
cat('<embed src="./Lecture notes/Chapter 4_7.pdf" 
    type="application/pdf" 
    width="100%" height="400px" />')
```

+ Chapter 5: 
  + Friedman test for General Alternatives in a Randomized Complete Block Design
```{r, echo=FALSE, out.width = '800px', out.height = '400px', results='asis'}
cat('<embed src="./Lecture notes/Chapter 5_1.pdf" 
    type="application/pdf" 
    width="100%" height="400px" />')
```

  + Two-Sided All-Treatments Multiple Comparisons for General Alternative in a Randomized Complete Block Design 
```{r, echo=FALSE, out.width = '800px', out.height = '400px', results='asis'}
cat('<embed src="./Lecture notes/Chapter 5_2.pdf" 
    type="application/pdf" 
    width="100%" height="400px" />')
```

  + Mack-Skillings test for General Alternatives in a Randomized Block Design with Equal Number of Replications Per treatment-Block Combination 
```{r, echo=FALSE, out.width = '800px', out.height = '400px', results='asis'}
cat('<embed src="./Lecture notes/Chapter 5_3.pdf" 
    type="application/pdf" 
    width="100%" height="400px" />')
```

  + Two-Sided All-Treatments Multiple Comparisons for General Alternative in a Randomized Block Design with Equal Number of Replications Per treatment-Block Combination
```{r, echo=FALSE, out.width = '800px', out.height = '400px', results='asis'}
cat('<embed src="./Lecture notes/Chapter 5_4.pdf" 
    type="application/pdf" 
    width="100%" height="400px" />')
```

+ Chapter 6: 
  + Intro to Bootstrap 
```{r, echo=FALSE, out.width = '800px', out.height = '400px', results='asis'}
cat('<embed src="./Lecture notes/Chapter 6_1.pdf" 
    type="application/pdf" 
    width="100%" height="400px" />')
```

  + Bootstrap Confidence Intervals  
```{r, echo=FALSE, out.width = '800px', out.height = '400px', results='asis'}
cat('<embed src="./Lecture notes/Chapter 6_2.pdf" 
    type="application/pdf" 
    width="100%" height="400px" />')
```
  